\documentclass[12pt]{report}


\begin{document}

\section*{Design}

\subsection*{Overview}

\subsubsection*{Objectives}
LLNMS seeks to achieve the following objectives
\begin{declarative}
\item A comprehensive suite of tools and options.
\item Absolute minimalism in design and requirements.  LLNMS should run on a basic installation with no additional tools.  Additional tools should provide upgraded functionality.
\item [Modular design: ] LLNMS executables should be independent of each other and allow for customization without damaging the core operation. 
\end{declarative}

\subsubsection*{Networks}

LLNMS allows you to scan a network to view all available or detected assets.  This 
can be used to monitor the health of a network infrastructure or to detect intruders into
a system.  To implement this capability, LLNMS scans a network using a specified set of 
rules.  

\section*{Executables}
\subsection*{\texttt{llnms-scan-networks}}
This is the primary network scanning function for llnms.  This tool takes a list of network assets
in \texttt{\$LLNMS\_HOME/networks} and checks for their existence on the network.  This then outputs the 
status to the status file in \texttt{\$LLNMS\_HOME/run/llnms-network-status.txt}. Unless you have identified
specific host assets to scan, this is the only way to identify new assets to inspect. 

\subsection*{\texttt{llnms-scan-assets}}
This is the specific network host asset scanning tool.  This takes a list of assets identified by the user or
hosts which are currently available on the networks and seeks to scan specific information about them.

\section*{Hierarchy}

LLNMS operates as an independent set of utilities which depend on 
a deterministic file and directory structure. 

\subsubsection*{LLNMS\_HOME}
This is the base directory for which all LLNMS activity takes place.  This
contains all configuration files, utilities, and output.  On linux systems, 
the designated home is at \texttt{/var/tmp/llnms}. 

\subsubsection*{LLNMS\_HOME/bin}
This is the binary and script directory for all executable programs in LLNMS.  This
should be added to your path in order to ensure that LLNMS is available to the user.

\subsubsection*{LLNMS\_HOME/networks}
This is the location where all network definitions are stored.

\section*{Installation}

\subsection*{Linux}

\subsubsection*{LLNMS-NetView}
In order to install LLNMS-NetView onto your system, you will need node.js installed. In Ubuntu apt, 
this can be done via \texttt{apt-get install nodejs}.

\end{document}
